---
title: "assignment4plus"
author: "Keliang Xu"
date: "12/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(stringr)
library(tidytext)
library(gutenbergr)
library(tidyr)
library(textdata)
library(RColorBrewer)
library(wordcloud)
library(reshape2)
library(ggplot2)

library(tnum)
library(knitr)
library(kableExtra)
library(tnum)
library(sentimentr)
library(ggpubr)
```

## Sentence-level Analysis

### Tnum ingester

```{r,warning=FALSE,message=FALSE}
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")

source("Book2TN-v6A-1.R")

Holmes<-gutenberg_download(2852)
#write.table(Holmes, file = "holmes.txt", sep = "\t",row.names = F, col.names = T)

Holmes_txt<-read.table("Holmes.txt",header = T)
```

I have the same method in assignment4 to get the holmes text from TN and gutenberg.
This time I will put some visualization into report.

### Sentimerntr 

The average sentiment score of the sentences in the review. 
The most interesting variable is the ave_sentiment, which is the sentiment of the review in
one number. The number can take positive or negative values and expresses the valence and the
polarity of the sentiment.


```{r}
q<- tnum.query("holmes/hound# has text", max = 2900) 
df <-tnum.objectsToDf(q)
para_text <- df %>% pull(string.value) %>% 
                    str_replace_all("\"","") %>% 
                    str_flatten(collapse = " ")

hound<-get_sentences(para_text)
hound_sentiment<-sentiment(hound)

hist(hound_sentiment$sentiment)
df %>% 
  get_sentences() %>% 
  sentiment_by(by = NULL) %>% #View()
  ggplot() + geom_density(aes(ave_sentiment))
```

Next analyze the sentiment scores and look at some summary statistics of the calculated sentiment scores.

```{r,warning=FALSE,message=FALSE}
sentiment_raw<-sentiment_by(Holmes$text)
sentiment_by(para_text)
summary(sentiment_raw$ave_sentiment)
qplot(sentiment_raw$ave_sentiment,
geom="histogram",binwidth=0.1,main="Review Sentiment Histogram with raw data")

sentiment_pro <-df %>% 
  get_sentences() %>% 
  sentiment_by(by = NULL)
qplot(sentiment_pro$ave_sentiment,
geom="histogram",binwidth=0.1,main="Review Sentiment Histogram with processing data")
```
Comparing these two plots, we can find that if the text is not processed, there will be a lot of 0 values, because it is similar to a chapter or a blank line will be doubled as 0.

## Sentence analysis compare to Task two 


### Sentence analysis by BING sentiment lexicon

I analyzed each sentence word by word and got sentiment score for word analysis.
Comparing with Bing sentiment lexicon word analysis.

```{r,warning=FALSE,message=FALSE}
word_df<-df %>% select(subject,property,string.value)
word_df<-cbind(word_df,bing=0)
tmp<-NA
for(i in 1:length(df$subject)){
  tmp<-word_df$string.value[i]
  tmp<-data.frame(tmp)
 
   tidy_tmp <- tmp %>%
    mutate(
     chapter = cumsum(str_detect(tmp, regex("^chapter [\\divxlc]", ignore_case = TRUE)))
  )%>%
  unnest_tokens(word,tmp) %>%
  anti_join(stop_words)
  
  tmp_sentiment <- tidy_tmp %>%
  inner_join(get_sentiments("bing")) 
  
  word_df$bing[i]<-sum(tmp_sentiment$sentiment=="positive")-sum(tmp_sentiment$sentiment=="negative")
}
```

Next I'll use Task two method to analysis the sentence. I will separate the words from each sentence and compare to which just use function sentiment_by().


```{r,warning=FALSE}
plot_holmes<- cbind(element_id=sentiment_pro$element_id,sentiment=word_df$bing)
plot_holmes<- cbind(plot_holmes,group="bing")
plot_2<-cbind(element_id=sentiment_pro$element_id,sentiment=sentiment_pro$ave_sentiment)
plot_2<-cbind(plot_2,group="Sentimerntr")
plot_holmes<-rbind(plot_holmes,plot_2)

plot_holmes<-data.frame(plot_holmes)

for(i in 1:length(plot_holmes$element_id)){
  plot_holmes$sentiment[i]<-round(as.numeric(plot_holmes$sentiment[i]),2)
}
plot_holmes$element_id<-as.numeric(plot_holmes$element_id)
plot_holmes$sentiment<-as.numeric(plot_holmes$sentiment)

p1<-ggplot(plot_holmes[1:2865,] ) +
  geom_col(aes(element_id, sentiment),show.legend = FALSE,color="RED") + 
  ggtitle("sentence-level with BING words by words")

p2<-ggplot(plot_holmes[2866:5730,])+
  geom_col(aes(element_id, sentiment) ,show.legend = FALSE,color="BLUE")  + 
  ggtitle("sentence-level analysis")
ggpubr::ggarrange(p1,p2,nrow=2,ncol=1)

ggplot(plot_holmes, aes(element_id, sentiment,color=group)) +
  geom_col(show.legend = FALSE) 
```

### Sentence analysis by NRC sentiment lexicon

Comparing with NRC index word analysis.

```{r,warning=FALSE,message=FALSE}
word_df<-df %>% select(subject,property,string.value)
word_df<-cbind(word_df,nrc=0)
tmp<-NA
for(i in 1:length(df$subject)){
  tmp<-word_df$string.value[i]
  tmp<-data.frame(tmp)
  tidy_tmp <- tmp %>%
    mutate(
     chapter = cumsum(str_detect(tmp, regex("^chapter [\\divxlc]", ignore_case = TRUE)))
  )%>%
  unnest_tokens(word,tmp) %>%
  anti_join(stop_words)
  
  tmp_sentiment <- tidy_tmp %>%
  inner_join(get_sentiments("nrc"))  %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
  
  word_df$nrc[i]<-sum(tmp_sentiment$sentiment=="positive")-sum(tmp_sentiment$sentiment=="negative")
}
```

```{r,warning=FALSE}
plot_holmes<- cbind(element_id=sentiment_pro$element_id,sentiment=word_df$nrc)
plot_holmes<- cbind(plot_holmes,group="nrc")
plot_2<-cbind(element_id=sentiment_pro$element_id,sentiment=sentiment_pro$ave_sentiment)
plot_2<-cbind(plot_2,group="Sentimerntr")
plot_holmes<-rbind(plot_holmes,plot_2)

plot_holmes<-data.frame(plot_holmes)

for(i in 1:length(plot_holmes$element_id)){
  plot_holmes$sentiment[i]<-round(as.numeric(plot_holmes$sentiment[i]),2)
}
plot_holmes$element_id<-as.numeric(plot_holmes$element_id)
plot_holmes$sentiment<-as.numeric(plot_holmes$sentiment)

p1<-ggplot(plot_holmes[1:2865,] ) +
  geom_col(aes(element_id, sentiment),show.legend = FALSE,color="RED") + 
  ggtitle("sentence-level with NRC words by words")

p2<-ggplot(plot_holmes[2866:5730,])+
  geom_col(aes(element_id, sentiment) ,show.legend = FALSE,color="BLUE")  + 
  ggtitle("sentence-level analysis")
ggpubr::ggarrange(p1,p2,nrow=2,ncol=1)

ggplot(plot_holmes, aes(element_id, sentiment,color=group)) +
  geom_col(show.legend = FALSE) 
```

### Sentence analysis by AFINN sentiment lexicon

Comparing with AFINN index word analysis.

```{r,warning=FALSE,message=FALSE}
word_df<-df %>% select(subject,property,string.value)
word_df<-cbind(word_df,afinn=0)
tmp<-NA
for(i in 1:length(df$subject)){
  tmp<-word_df$string.value[i]
  tmp<-data.frame(tmp)
  tidy_tmp <- tmp %>%
    mutate(
     chapter = cumsum(str_detect(tmp, regex("^chapter [\\divxlc]", ignore_case = TRUE)))
  )%>%
  unnest_tokens(word,tmp) %>%
  anti_join(stop_words)
  
  tmp_sentiment <- tidy_tmp %>%
  inner_join(get_sentiments("afinn")) 
                 
  
  word_df$afinn[i]<-sum(tmp_sentiment$value)-length(tmp_sentiment$value)
}
```

```{r,warning=FALSE}
plot_holmes<- cbind(element_id=sentiment_pro$element_id,sentiment=word_df$afinn)
plot_holmes<- cbind(plot_holmes,group="affin")
plot_3<-cbind(element_id=sentiment_pro$element_id,sentiment=sentiment_pro$ave_sentiment)
plot_3<-cbind(plot_3,group="Sentimerntr")
plot_holmes<-rbind(plot_holmes,plot_3)

plot_holmes<-data.frame(plot_holmes)

for(i in 1:length(plot_holmes$element_id)){
  plot_holmes$sentiment[i]<-round(as.numeric(plot_holmes$sentiment[i]),2)
}
plot_holmes$element_id<-as.numeric(plot_holmes$element_id)
plot_holmes$sentiment<-as.numeric(plot_holmes$sentiment)

p1<-ggplot(plot_holmes[1:2865,] ) +
  geom_col(aes(element_id, sentiment),show.legend = FALSE,color="RED") + 
  ggtitle("sentence-level with AFINN words by words")

p2<-ggplot(plot_holmes[2866:5730,])+
  geom_col(aes(element_id, sentiment) ,show.legend = FALSE,color="BLUE")  + 
  ggtitle("sentence-level analysis")
ggpubr::ggarrange(p1,p2,nrow=2,ncol=1)

ggplot(plot_holmes, aes(element_id, sentiment,color=group)) +
  geom_col(show.legend = FALSE) 
```

### Sentence analysis by LOUGHRAN sentiment lexicon

Comparing with LOUGHRAN index word analysis.

```{r,warning=FALSE,message=FALSE}
word_df<-df %>% select(subject,property,string.value)
word_df<-cbind(word_df,loughran=0)
tmp<-NA
for(i in 1:length(df$subject)){
  tmp<-word_df$string.value[i]
  tmp<-data.frame(tmp)
  tidy_tmp <- tmp %>%
    mutate(
     chapter = cumsum(str_detect(tmp, regex("^chapter [\\divxlc]", ignore_case = TRUE)))
  )%>%
  unnest_tokens(word,tmp) %>%
  anti_join(stop_words)
  
  tmp_sentiment <- tidy_tmp %>%
  inner_join(get_sentiments("loughran")) %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
  
  word_df$loughran[i]<-sum(tmp_sentiment$sentiment=="positive")-sum(tmp_sentiment$sentiment=="negative")
}
```

```{r,warning=FALSE}
plot_holmes<- cbind(element_id=sentiment_pro$element_id,sentiment=word_df$loughran)
plot_holmes<- cbind(plot_holmes,group="loughran")
plot_4<-cbind(element_id=sentiment_pro$element_id,sentiment=sentiment_pro$ave_sentiment)
plot_4<-cbind(plot_4,group="Sentimerntr")
plot_holmes<-rbind(plot_holmes,plot_4)

plot_holmes<-data.frame(plot_holmes)

for(i in 1:length(plot_holmes$element_id)){
  plot_holmes$sentiment[i]<-round(as.numeric(plot_holmes$sentiment[i]),2)
}
plot_holmes$element_id<-as.numeric(plot_holmes$element_id)
plot_holmes$sentiment<-as.numeric(plot_holmes$sentiment)

p1<-ggplot(plot_holmes[1:2865,] ) +
  geom_col(aes(element_id, sentiment),show.legend = FALSE,color="RED") + 
  ggtitle("sentence-level with loughran words by words")

p2<-ggplot(plot_holmes[2866:5730,])+
  geom_col(aes(element_id, sentiment) ,show.legend = FALSE,color="BLUE")  + 
  ggtitle("sentence-level analysis")
ggpubr::ggarrange(p1,p2,nrow=2,ncol=1)

ggplot(plot_holmes, aes(element_id, sentiment,color=group)) +
  geom_col(show.legend = FALSE) 
```
